Self Regulation Ontology Retest Analyses

### 2018-12-12 code/analysis_nbs/ResponseToReviewers.Rmd

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r}
library(tidyverse)
library(jsonlite)

workspace_scripts = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/'

source(paste0(workspace_scripts,'SRO_Retest_Analyses_Helper_Functions.R'))

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'

fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'

source(paste0(workspace_scripts, 'battery_completion_data.R'))

source(paste0(workspace_scripts,'lit_review_data.R'))

source(paste0(workspace_scripts,'subject_data.R'))

source(paste0(workspace_scripts,'intratrial_rel_data.R'))

source(paste0(workspace_scripts,'demog_data.R'))

source(paste0(workspace_scripts,'boot_rel_data.R'))

source(paste0(workspace_scripts,'rel_comp_data.R'))

source(paste0(workspace_scripts,'duplicate_items_data.R'))

source(paste0(workspace_scripts,'measure_labels_data.R'))

source(paste0(workspace_scripts,'meaningful_vars_data.R'))

source(paste0(workspace_scripts,'bayesian_models_data.R'))
```

#R1

##R1.5
>If the common assumption that threshold and non-decision time do not vary between conditions in tasks with intermixed trials is true, we could interpret the contrasts between those parameters generated from the EZ diffusion model to simply be noise. If that were the case, we shouldn't expect those contrasts to be reliable.

TODO: Check if EZ contrast estimates are >0

```{r}

```

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC)
- make new `boot_df` (with both types of ICC)
- rerun MCMC models with ICC(2,1)

```{r}

```

##R1.7
>It is stated on pg. 9 that the ICC ranges from -1 to 1. Though statistical packages report negative ICCs, it is sometimes suggested that they should be treated as zero (e.g. Bartko, 1976), as a proportion of variance cannot theoretically be negative. I am unsure what the best approach is for the current purposes, but I note it for consideration. As there don't appear to be a large number of negative ICCs, I suspect it wouldn't affect the averages much.

TODO:
- report how many negative ICC's there are
- run all analyses that include ICC's with 
  - replacing negative values with 0's 
  - removing them

```{r}

```

##R1.8
>I think it is a strength of the paper overall that the authors consider the importance of trial numbers, though I'm curious why they chose the number of trials they did for their tasks (e.g. if they came from particular studies or an average)? The role of trial numbers was also something we were interested in (see our Supplementary material D: https://link.springer.com/article/10.3758/s13428-017-0935-1#SupplementaryMaterial), and is discussed by Rouder & Haaf (2018).

TODO:
- extract trial numbers for papers that went in to the lit search and compare to ours
- code pipeline to get reliability with k number of trials

```{r}

```

#R2

##R2.1
>The researchers were careful in their sampling procedure to try to minimize differences between participants who completed (vs. did not complete) the retest phase of the test-retest. Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
from_gh =FALSE

library(tidyverse)
library(jsonlite)

cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_bw())
ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")

@@

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'

fig_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/'

source(paste0(workspace_scripts,'lit_review_data.R'))

# source(paste0(workspace_scripts,'subject_data.R'))
# 
# source(paste0(workspace_scripts,'boot_rel_data.R'))
# 
# source(paste0(workspace_scripts,'measure_labels_data.R'))
```

@@

#R1

##R1.5
>If the common assumption that threshold and non-decision time do not vary between conditions in tasks with intermixed trials is true, we could interpret the contrasts between those parameters generated from the EZ diffusion model to simply be noise. If that were the case, we shouldn't expect those contrasts to be reliable.

TODO: 
### Are EZ contrast estimates are >0?

Yes. The assumption that thresholds and non-decision times are the same across conditions does not hold in our data as the distributions of these parameters are systematically different than 0 for both time point.

```{r}
if(from_gh){
  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_DDM_Analyses/master/code/workspace_scripts/g_legend.R', ssl.verifypeer = FALSE)))
}else{
  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_subject_data.R')
}
```

```{r}
ez_contrast_vars = measure_labels %>%
  filter(raw_fit == "EZ" & overall_difference == "contrast") %>%
  select(dv)
```

```{r}
get_tval = function(x, val=0){
  return((mean(x, na.rm=T) - val)/(sd(x, na.rm=T)/sqrt(length(x))))
}

get_mean = function(x){
  return(mean(x, na.rm=T))
}
```

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  gather(key, value) %>%
  group_by(key) %>%
  summarise(tvals = get_tval(value), 
            means = get_mean(value))
```

```{r}
test_data_522 %>%
  select(ez_contrast_vars$dv) %>%
  gather(key, value) %>%
  group_by(key) %>%
  summarise(tvals = get_tval(value), 
            means = get_mean(value))
```

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  ggplot(aes(value))+
  geom_density(aes(group=dv, col=rt_acc), linetype="dotted")+
  geom_density(aes(col=rt_acc), size=2.5)+
  xlim(-1.5,1.5)+
  geom_vline(xintercept=0, linetype="dashed", size=1.5)+
  theme(legend.title=element_blank())+
  xlab("")+
  ylab("")+
  facet_wrap(~time)
```

### Are their reliabilities >0?

... Although the thresholds and non-decision times for contrasts are >0 they are still not reliable

*Response:* Measures do not have to be noise to be unreliable. In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of noise. Still these measures are not reliable si
similar to differences in raw measures of response times and accuracies.

@@

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC)
- make new `boot_df` (with both types of ICC)
- rerun MCMC models with ICC(2,1)

```{r}
'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_DDM_Analyses/code/workspace_scripts/ddm_measure_labels.R'
```

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
from_gh =FALSE

library(tidyverse)
library(jsonlite)

cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_bw())
ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")
```

@@

#R1

##R1.5
>If the common assumption that threshold and non-decision time do not vary between conditions in tasks with intermixed trials is true, we could interpret the contrasts between those parameters generated from the EZ diffusion model to simply be noise. If that were the case, we shouldn't expect those contrasts to be reliable.

TODO: 
### Are EZ threshold and non-decision time contrast estimates are >0?

@@

```{r}
ez_contrast_vars = measure_labels %>%
  filter(raw_fit == "EZ" & overall_difference == "contrast") %>%
  select(dv)
```

```{r}
get_tval = function(x, val=0){
  return((mean(x, na.rm=T) - val)/(sd(x, na.rm=T)/sqrt(length(x))))
}

get_mean = function(x){
  return(mean(x, na.rm=T))
}
```

Means and and T values comparing the means to 0 for T1 data.

Means and and T values comparing the means to 0 for T2 data.

@@

Means and and T values comparing the means to 0 for T2 data.

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  gather(key, value) %>%
  group_by(key) %>%
  summarise(tvals = get_tval(value), 
            means = get_mean(value))
```

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  ggplot(aes(value))+
  geom_density(aes(group=dv, col=rt_acc), linetype="dotted")+
  geom_density(aes(col=rt_acc), size=2.5)+
  xlim(-1.5,1.5)+
  geom_vline(xintercept=0, linetype="dashed", size=1.5)+
  theme(legend.title=element_blank())+
  xlab("")+
  ylab("")+
  facet_wrap(~time)
```

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  group_by(rt_acc, time) %>%
  summarise(tvals=get_tval(value),
            means=get_mean(value))
```

@@

### Are their reliabilities >0?

... Although the thresholds and non-decision times for contrasts are >0 they are still not reliable

```{r}
rt_ddm_vars = measure_labels %>%
  filter(overall_difference %in% c("non-contrast", "contrast")) %>%
  select(dv)

if(from_gh){
  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/make_rel_df.R', ssl.verifypeer = FALSE)))
}else{
  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
}
```

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd

if(from_gh){
  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/make_rel_df.R', ssl.verifypeer = FALSE)))
}else{
  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
}
```

*Response:* Measures do not have to be noise to be unreliable. In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of noise. Still these measures are not reliable si
similar to differences in raw measures of response times and accuracies.

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- [DONE] recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC)
- make new `boot_df` (with both types of ICC)
- rerun MCMC models with ICC(2,1)

### 2018-12-13 code/SRO_Retest_Analyses.Rmd
working on response to reviewers

```{r}
demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc = quantile(icc, probs=0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975)) %>%
  arrange(-median_icc)
```

@@

```{r}
demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))

demog_rel_df %>%
  select(dv, icc) %>%
  arrange(-icc)
```

@@

demog_rel_df %>%
  mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
  ggplot(aes(icc, fill = factor(timed)))+
  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Count")+
  scale_fill_manual(values = c("grey", "grey25"))+
  theme(legend.position = "none")
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean ICC")+
  ylim(-0.4,1)
```

@@

sample one row per measure out of lit review
r^2 of retest_reliability ~ sampled_reliability vs.
r^2 of retest_reliability ~ mean_icc

coef of retest_reliability ~ sampled_reliability vs.
coef of retest_reliability ~ mean_icc

@@

Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen. Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman). The bootstrapped version is essentially the same but the plots are busier due to more datapoints.

```{r}
rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))

rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
```

@@

```{r}
cor(rel_df[,c('spearman', 'icc', 'pearson')])
```

Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.

@@

```{r message=FALSE, warning=FALSE}
boot_df %>%
  group_by(dv) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

@@

boot_df %>%
  group_by(task) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r eval=FALSE}
summary(icc_by_task_model)
```

```{r echo=FALSE}
rm(icc_by_task_model)
```

@@

The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al. (2017), lies in the difference in sources of variance between these measures. Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance. Thus, measures with high between subjects variance would have high test-retest reliability. Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
```

@@

Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

summary(icc_by_num_trials_model)
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
```

@@

```{r}
summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
```

@@

```{r}
summary(icc_by_rawfit_noncon_model)
```

@@

```{r}
summary(icc_by_rawfit_con_model)
```

```{r echo=FALSE}
rm(icc_by_rawfit_con_model, icc_by_rawfit_noncon_model)
```

@@

```{r}
tmp %>%
  group_by(contrast) %>%
  summarise(mean_icc = mean(icc),
            sd_icc = sd(icc))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

tmp_save = tmp %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
```

@@

Does number of items in a survey have a significant effect on the average ICC of survey measures? No.

```{r warning=FALSE, message=FALSE}
summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

>>>>

```{r}
demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc3.k = quantile(icc3.k, probs=0.5),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975)) %>%
  arrange(-median_icc3.k)
```

@@

```{r}
demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc3.k'))

demog_rel_df %>%
  select(dv, icc3.k) %>%
  arrange(-icc3.k)
```

@@

demog_rel_df %>%
  mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
  ggplot(aes(icc3.k, fill = factor(timed)))+
  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
  xlab("icc3.k")+
  ylab("Count")+
  scale_fill_manual(values = c("grey", "grey25"))+
  theme(legend.position = "none")
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean icc3.k")+
  ylim(-0.4,1)
```

@@

sample one row per measure out of lit review
r^2 of retest_reliability ~ sampled_reliability vs.
r^2 of retest_reliability ~ mean_icc3.k

coef of retest_reliability ~ sampled_reliability vs.
coef of retest_reliability ~ mean_icc3.k

@@

Though we are primarily reporting icc3.k's as our metric of reliability the results don't change depending on the metric chosen. Here we plot point estimates of three different reliability metrics against each other (icc3.k, Pearson, Spearman). The bootstrapped version is essentially the same but the plots are busier due to more datapoints.

```{r}
rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc3.k', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))

rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc3.k, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
```

@@

```{r}
cor(rel_df[,c('spearman', 'icc3.k', 'pearson')])
```

Note: Some variables have <0 icc3.k's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.

@@

```{r message=FALSE, warning=FALSE}
boot_df %>%
  group_by(dv) %>%
  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc3.k_median', 'icc3.k_2.5', 'icc3.k_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

@@

boot_df %>%
  group_by(task) %>%
  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc3.k_median', 'icc3.k_2.5', 'icc3.k_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r eval=FALSE}
summary(icc3.k_by_task_model)
```

```{r echo=FALSE}
rm(icc3.k_by_task_model)
```

@@

The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al. (2017), lies in the difference in sources of variance between these measures. Specifically, the icc3.k is calculated as the ratio of variance between subjects variance to all sources of variance. Thus, measures with high between subjects variance would have high test-retest reliability. Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc3.k = median(icc3.k),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc3.k)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_icc3.k','icc3.k_2.5','icc3.k_97.5'), digits=3)
```

@@

Does number of items in a task have a significant effect on the average icc3.k of meaningful measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

summary(icc3.k_by_num_trials_model)
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc3.k))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("icc3.k")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv')

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc3.k_median = quantile(icc3.k, probs = 0.5),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
            num_vars = n()/1000)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('icc3.k_median', 'icc3.k_2.5', 'icc3.k_97.5'), digits=3)
```

@@

```{r}
summary(lmerTest::lmer(icc3.k ~ contrast + (1|dv) ,tmp))
# summary(MCMCglmm(icc3.k ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
```

@@

```{r}
summary(icc3.k_by_rawfit_noncon_model)
```

@@

```{r}
summary(icc3.k_by_rawfit_con_model)
```

```{r echo=FALSE}
rm(icc3.k_by_rawfit_con_model, icc3.k_by_rawfit_noncon_model)
```

@@

```{r}
tmp %>%
  group_by(contrast) %>%
  summarise(mean_icc3.k = mean(icc3.k),
            sd_icc3.k = sd(icc3.k))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc3.k")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

tmp_save = tmp %>%
  group_by(task_name) %>%
  summarise(median_icc3.k = median(icc3.k),
            icc3.k_2.5 = quantile(icc3.k, probs = 0.025),
            icc3.k_97.5 = quantile(icc3.k, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc3.k)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('median_icc3.k', 'icc3.k_2.5','icc3.k_97.5'), digits=3)
```

@@

Does number of items in a survey have a significant effect on the average icc3.k of survey measures? No.

```{r warning=FALSE, message=FALSE}
summary(lmerTest::lmer(icc3.k ~ num_all_trials + (1|dv), data = tmp))
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc3.k))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("icc3.k")
```
